\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-10-02 gwnnDraft02.tex
refs

\section{Introduction} 
\label{sec:intro} 
The recent experimental detection of gravitational waves~\cite{Abbott:2016blz} gives humanity a new way to observe the universe. Future experiments~\cite{Seto:2001qf,Crowder:2005nr,Harry:2006fi,Sathyaprakash:2012jk,Janssen:2014dka,2017arXiv170200786A,Sato:2017dkf} will greatly expand the frequency range observable. Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{Witten:1984rs,Hogan:1984hx,Hogan:1986qda,PhysRevLett.65.3080,Caprini:2015zlo,Mazumdar:2018dfl}. Thus, searches for this background of gravitational waves can give direct information of the history of the universe before big bang nucleosynthesis. 
Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation. This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Jaeckel:2016jlh,Addazi:2016fbj,Hardy:2016mns,Dienes:2016vei,Tsumura:2017knk,Acharya:2017szw,Bernal:2017kxu,Aoki:2017aws,Heikinheimo:2018esa,Geller:2018mwu,Croon:2018erz,Baldes:2018emh,Bai:2018dxf,Breitbach:2018ddu,Fairbairn:2019xog,Helmboldt:2019pan,Caputo:2019wsd,Bertone:2019irm}.

@@

\begin{figure*}[tb]
\centering
\begin{minipage}[c]{\textwidth}
\includegraphics[width=.45\textwidth ]{highest.png}
\hfill
\includegraphics[width=.45\textwidth]{TwoFar.png} 
\hfill
\includegraphics[width=.45\textwidth]{TwoMed.png} 
\hfill
\includegraphics[width=.45\textwidth]{energydensity.png} 
\end{minipage}
\hfill
\caption{ Gravitational wave power spectrum for various models. The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures. The bottom left (right) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$). All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa (blue), DECIO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
\label{fig:Haa}
\end{figure*}

@@

The spectral noise curves used to create the PLI curves shown in Figs.~\ref{fig::Nnatural} and \ref{fig:Haa} were taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and ~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array. We have assumed an observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA. In the case of the PTA experiments, the sensitivity curves are dependent on how frequently the pulsar's timing residuals, $\delta t$, are measured. When using Eq.~(\ref{eqn::SNR}) to construct the PSI curves for SKA, the upper integration bound is inversely proportional to pulsar's timing residual, $f_{min} = 1/\delta t$. In this work, it is assumed that $\delta t = 14$ days, but this may underestimate the capabilities of SKA as well as the cadences of the pulsar populations. If the timing residuals are lowered the maximum frequency reach of SKA increases, and the corresponding PSI curves in Figs.~(\ref{fig::Nnatural}) $\&$ ~(\ref{fig:Haa}) are shifted to the right, possibly giving the PTAs sensitivity to some of the scenarios considered here.

>>>>

\section{Introduction} 
\label{sec:intro} 
The recent experimental detection of gravitational waves~\cite{Abbott:2016blz} gives humanity a new way to observe the universe. Future experiments~\cite{Danzmann:1994mma,Seto:2001qf,Crowder:2005nr,PhysRevD.72.083005,Harry:2006fi,Sathyaprakash:2012jk,Janssen:2014dka,Audley:2017drz,2017arXiv170200786A,Sato:2017dkf,Sato_2017,10.1093/ptep/pty078} will greatly expand the frequency range observable. Thus far, experiments have only observed recent events such as black hole mergers, but phase transitions in the early universe can leave an imprint as a \textit{stochastic} gravitational wave background~\cite{Witten:1984rs,Hogan:1984hx,Hogan:1986qda,PhysRevLett.65.3080,Caprini:2015zlo,Mazumdar:2018dfl}. Thus, searches for this background of gravitational waves can give direct information of the history of the universe before big bang nucleosynthesis. 
Because gravity is universal, gravitational waves can allow us to probe hidden sectors that couple very weakly, or not at all, to the Standard Model as long they are reheated after inflation. This was first explored in~\cite{Schwaller:2015tja}, and there has been significant work on this idea since~\cite{Jaeckel:2016jlh,Addazi:2016fbj,Hardy:2016mns,Dienes:2016vei,Tsumura:2017knk,Acharya:2017szw,Bernal:2017kxu,Aoki:2017aws,Heikinheimo:2018esa,Geller:2018mwu,Croon:2018erz,Baldes:2018emh,Bai:2018dxf,Breitbach:2018ddu,Fairbairn:2019xog,Helmboldt:2019pan,Caputo:2019wsd,Bertone:2019irm}.

@@

\begin{figure*}[tb]
\centering
\begin{minipage}[c]{\textwidth}
\includegraphics[width=.45\textwidth ]{highest.png}
\hfill
\includegraphics[width=.45\textwidth]{TwoFar.png} 
\hfill
\includegraphics[width=.45\textwidth]{TwoMed.png} 
\hfill
\includegraphics[width=.45\textwidth]{energydensity.png} 
\end{minipage}
\hfill
\caption{ Gravitational wave power spectrum for various models. The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures. The bottom left (right) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$). All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa~\citep{Audley:2017drz} (blue), DECIO (light blue)~\citep{10.1093/ptep/pty078}, BBO (red)~\citep{PhysRevD.72.083005} , SKA~\cite{Janssen:2014dka} 5-year (purple), SKA 10-year (orange), SKA 20-year (green).   }
\label{fig:Haa}
\end{figure*}

@@

The spectral noise curves used to create the PLI curves shown in Figs.~\ref{fig::Nnatural} and \ref{fig:Haa} were taken from~\citep{Robson_2019,PhysRevD.83.084036,doi:10.1142/S0218271813410137,10.1093/ptep/pty078, Breitbach:2018ddu} for the interferometers, and~\citep{Breitbach:2018ddu, Janssen:2014dka} for the SKA pulsar timing array. We have assumed an observation time of $T = 4 $ years for the interferometers and $T= 5, 10, 20 $  years for the various stages of SKA. In the case of the PTA experiments, the sensitivity curves are dependent on how frequently the pulsar's timing residuals, $\delta t$, are measured. When using Eq.~(\ref{eqn::SNR}) to construct the PSI curves for SKA, the upper integration bound is inversely proportional to pulsar's timing residual, $f_{min} = 1/\delta t$. In this work, it is assumed that $\delta t = 14$ days, but this may underestimate the capabilities of SKA as well as the cadences of the pulsar populations. If the timing residuals are lowered the maximum frequency reach of SKA increases, and the corresponding PSI curves in Figs.~(\ref{fig::Nnatural}) $\&$ ~(\ref{fig:Haa}) are shifted to the right, possibly giving the PTAs sensitivity to some of the scenarios considered here.
